Communication complexity: Chapter 7 \\ Multiparty communication

### 2019-03-15 CS860-CommunicationComplexity/assignments/Chapter7.tex
draft 2

\begin{proof}
\replacethistext{Enter your proof here.}
\end{proof}

@@

\end{proof}

>>>>

\begin{proof}
We seek to upper bound $\disc_\mu(\GIP^k)$ by $2^{\frac{-n}{4^k}}$. Using the previous Theorem this yields the result. We proceed by induction on $k$. The base case, $k=2$, is satisfied by our bound on Chapter $3$ on $\IP$. So suppose $k>3$ and the  desired bound holds for smaller $k$. For function $f$, and cylindrical intersection $S\subseteq \calX^k$ we use $\disc_\mu^S(f)$ to denote the discrepancy of $S$:
$$\disc_\mu^S(f) = |\mu(S\cap f^{-1}(0)) - \mu(S\cap f^{-1}(1)))|.$$
Let $\mu^k$ be the uniform distribution over $\calX^k = (\{0,1\}^n)^k$. Let $S = S_1\times \dots \times S_k\subseteq \calX^k$ be a cylindrical intersection.
$$\disc_{\mu^k}^S(\GIP^k) = \sum_{i=1}^k\sum_{x^i \in S_i} \frac{1}{2^{nk}}(-1)^{\GIP^k(x^1\dots x^k)}.$$

Let $\text{proj}_{k-1}^{x^k}(x^1\dots x^k) = y^1\dots y^k$ where $y^j_i = x^j_i \wedge x^k_i$. Then
$$\GIP^k(x^1\dots x^k) = \GIP^{k-1}(\text{proj}_{k-1}^{x^k}(x^1\dots x^k)).$$
So we have
$$\disc_{\mu^k}^S(\GIP^k) = \sum_{x^k\in S_k}\frac{1}{2^n}\sum_{i=1}^{k-1}\sum_{x^i \in S_i}\frac{1}{2^{n(k-1)}}(-1)^{\GIP^{k-1}(\text{proj}_{k-1}^{x^k}(x^1\dots x^k))} = \sum_{x^k \in S_k}\frac{1}{2^n}\disc^{\text{proj}_{k-1}^{x^k}(S)}_{\mu^{k-1}}(\GIP^{k-1}). $$
We apply Cauchy-Schwarz and our inductive hypothesis obtaining...
\end{proof}

@@

Using this simplified protocol $\pi$ we...
\end{proof}
